\section{Mobile Application \textit{Connected.Football}}
\label{sec:Product}
\lhead{Mobile Application \textit{Connected.Football}}
This chapter explains the \textit{Connected.Football} application in detail. The \textit{Connected.Football} application is used by football coaches for planning and communication with the team. 

\subsection{Architecture}
The \textit{Connected.Football} application was created with \textit{React-Native}. \textit{React-Native} is based on the JavaScript library \textit{React} which is maintained by Facebook. \textit{React} can be used as a base for single-page websites and for mobile applications. 

\textit{Connected.Football} also uses \textit{GraphQL} as a database for storing the members, the training programs and other data. 

\subsubsection{\textit{React-Native}}
\textit{React-Native} was announced by Facebook in 2015 and is using the \textit{React} architecture to crate native Android and IOS applications. 

The working principles of \textit{React-Native} are basically the same as \textit{React} except that \textit{React-Native} uses native views. It runs in a background process (which interprets the \textit{JavaScript} written by the developers) directly on the end-device and communicates with the native platform via a serializable, asynchronous and batched bridge.

\subsubsection{\textit{GraphQL}}
\textit{GraphQL} is a query language for APIs and a run time for fulfilling those queries with existing data. \textit{GraphQL} provides a complete and understandable description of the data in your API, gives clients the power to ask for exactly what they need and nothing more, makes it easier to evolve APIs over time, and enables powerful developer tools.

